Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-26 paper/ms.tex
ms: incorporate LAH suggestions

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018
  and Sep~2022.  Our search of \nstarssearched\ K- and M-dwarfs with
  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
  of these discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
  class of object known, and probably also the most massive
  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
  objects are outliers among outliers; LP 12-502 for instance shows a
  recurring ``dip complex'' with a period and total duration that are
  fixed over more than 1{,}000 cycles, but which in detail exhibits
  anywhere from four to eight local minima per cycle.  LP 12-502 also
  displayed distinct superposed periods simultaneously, and showed
  drastic shape changes shortly after flares.  Broadly speaking, we
  find that none of the CQVs maintain a fixed light curve shape over
  timescales of more than a few hundred cycles, and we revisit the
  arguments for why transient corotating material is the most viable
  explanation.  In the future, we expect that our sample will
  facilitate modeling and observational efforts aimed at understanding
  these objects, and connecting them to the broader contexts of star,
  disk, and exoplanet evolution.  For instance, if the transiting
  material is dust, then the rate of dip evolution implies that of
  order an asteroid belt's worth of mass passes through these
  structures over their lifetime of $\approx$$10^8$ years.
\end{abstract}

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae \citep{2021isma.book.....B},
occultations by gas-rich circumstellar disks
\citep{2017MNRAS.470..202B}, and, in geometrically favorable
circumstances, eclipses by stars and planets
\citep{2010exop.book...55W}.  More exotic forms of optical variability
relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
both M-dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).

Data from K2 and TESS have yielded a new class of variable star whose
root cause is only beginning to become clear: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show nearly periodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
Some CQVs show up to eight local minima (dips) per cycle.  Most are
pre-main-sequence M-dwarfs without near-infrared excesses, ages of
$\approx$5-150 million years (Myr), and rotation periods of at most
two days; they are observed to be $\approx$1-3\% of M-dwarfs younger
than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
dips can be chromatic, with a reddening law plausibly consistent with
dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.

A few competing explanations for what causes the complex quasiperiodic
variability are shown in Figure~\ref{fig:f1}.  All young M-dwarfs are
spotted, which produces flux variations over characteristic timescales
of the rotation period, $P_{\rm rot}$, and its half-harmonic,
$0.5\,P_{\rm rot}$.  The observed dips occur over durations as short
as $0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded
for any object with sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations instead require sharp geometries
with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  The
``clump'' scenario invokes opaque dust clumps orbiting near the
Keplerian corotation radius, which periodically eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
scenario invokes long-lived condensations of cool and dense
marginally-ionized gas, embedded within the hotter corona, that would
be centrifugally supported near corotation
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
Such structures are analogous to quiescent prominences and filaments
seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
though at much larger relative distances from the stellar surface.  A
final possibility that has been suggested is one of a ``screen'', in
which the inner wall of a quiescent circumstellar disk blocks a
portion of the stellar surface to produce sudden dips whenever spots
come into view \citep{2019ApJ...876..127Z}.

@@

CQVs remain mysterious because they have been both hard to discover
and hard to characterize.   Discoverability is tied to rarity: CQVs
comprise $\approx$1\% of the youngest $\approx$1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CQVs have been reported to date
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
The known CQVs are correspondingly faint; the initial K2 discoveries
\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
distances $\gtrsim$100\,pc, yielding optical brightnesses of
$V$$\approx$15.5 to $V$$>$20.  This renders time-series spectroscopy
at high resolution out of reach for current facilities, despite its
potential utility in ruling between the models.

@@

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M-dwarfs, the TESS 2-minute data are
roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M-dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M-dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  This selection
function includes dwarf stars later than spectral types of
$\approx$K6V \citep{2013ApJS..208....9P} for which TESS can acquire
1\% relative precision photometry in 1 hour of observation
\citep{2015JATIS...1a4003R}.  The target sample therefore includes
\nstarssearched\ M-dwarfs and late-K dwarfs, down to $T$$<$16 and out
to $d$$<$150\,pc.

@@

With the effective temperatures and stellar radii from the SED fit, we
then estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M-dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for anomalous M-dwarf colors and sizes relative
to model predictions include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of younq
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
t \}$ as
\begin{equation}
  d^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
in order to assign equal importance to each dimension.  The preferred
model mass is then one that minimizes this distance, and is quoted in
Table~\ref{tab:thetable}.

@@

As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
catalog did not show infrared excesses in the WISE1-4 bands.
Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
we labeled two objects as having ``good'' infrared excesses (both W3
and W4), and three as ``possible'' infrared excess.

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
the brightest 27.  We have phased each sector to its own local minimum
because for most of the sources we do not know the period at the
precision necessary to be able to accurately propagate an ephemeris
over two years.

Of these 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of the
CQV phenomenon in one sector, and marginal or non-existent signs in the
other.  While there is subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  
Based on the fraction of sources overall that ``turned off'', the
observed shape evolution implies that CQVs have a duty cycle of
$\approx$75\%.
This type of correction is likely worth including in population-level
estimates of how intrinsically common CQVs are in the low-mass stellar
population \citep[e.g.][]{2022AJ....163..144G}.

@@

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.  Based on this range, the star's
period is stable to at least one minute ($\pm$0.017\,hr) over the
three year baseline.  However, in detail, a period shift of
$\pm$1\,minute would yield major phase drifts over the baseline; that
time interval corresponds to roughly 1/1000$^{\rm th}$ of a period,
and we have observed 1500 cycles.  The achievable period precision,
$\sigma_{\rm P}$, can be estimated as
\begin{equation}
  \sigma_{\rm P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline
and $\sigma_{\phi}$ the phase precision with which any one feature
(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
tracked.  Assuming $\sigma_{\phi} \approx 0.01$ yields an expected
period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec} \approx
1.2\times 10^{-4}\,{\rm hr}$.  By visually fine-tuning over a grid in
period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which seems to
track certain features in the LP 12-502 light curve over its entire
baseline.

What exactly is observed?  For the first 64 cycles, the star shows a
pattern reminiscent of an eclipsing binary, with four obvious local
minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
-0.08, 0, 0.25 \}$, respectively.  Over cycles 0 to 64, the depth of
dips 1 and 3 remain roughly fixed.  However dip 4 {\it decreases} in
depth by about 2\%, while dip 2 {\it increases} in depth, by about the
same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth
dip may also be emerging, in the main ``large'' dip group.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f7.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
      dark blue circles; \nmaybes\ ambiguous CQV candidates are light
      blue circles.  The top panels show the \nstarssearched\ target
      stars with 120-second cadence TESS data as the shaded gray
      background; darker regions correspond to a larger relative
      number of searched stars.  The lower-left panel compares the
      rotation--color distribution of CQVs against the rotation
      periods of K- and M-dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CQV periods, in
      units of hours.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

\subsection{Typical and extreme CQVs}
\label{subsec:extreme}
Figure~\ref{fig:catalogscatter} shows some of the derived properties
for our CQV catalog, and contrasts them against both the target star
sample (top panels), and the population of rotating stars in the Pleiades
from \citet{2016AJ....152..114R}.
Generally, CQVs are much younger than typical field stars. 
In terms of their rotation, relative to the Pleiades,
they are among the more rapidly rotating half of M-dwarfs.
The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
to $T$$=$16, is a consequence of the 120-second selection function,
not detection sensitivity.

@@

The most massive CQVs in our sample might represent an interesting new
regime.  To date, the only stars reported to show the CQV phenomenon
are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their CAMD
locations, and their membership in LCC.  Based on its light curve
morphology, TIC~405910546 should be studied in greater depth, to
confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
that it has some of the lowest amplitude dips.  While TIC~405754448
might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the depth of
the coherent dips present in the Sector~11 light curve imply that the
CQV signal is indeed from the apparent primary of the system.  Taken
in sum, both of these objects seem to suggest that the CQV phenomenon
extends up in mass to pre-main-sequence K-dwarfs.

@@

An instructive point of comparison is the rapidly rotating magnetic
B-star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
than in the red \citep{1977ApJ...216L..31H}.  Photometric and
spectroscopic observations of this star have been understood in terms
of a warped torus of circumstellar material, analogous to the
geometries we are discussing for much cooler M-dwarfs
\citep{1978ApJ...224L...5L,2005ApJ...630L..81T}.  This material
however is unlikely to be dust, due to the relevant sublimation
timescales.  The opacity is instead thought to be sourced from
bound-free absorption from neutral hydrogen
\citep{2005ApJ...630L..81T}, although to our best knowledge direct
evidence for this conclusion has yet to be acquired.  Separate and
smaller-amplitude emission in $\sigma$~Ori~E may also come from
electrons scattering photospheric light toward the observer when the
clouds are not in transit \citep{2022MNRAS.511.4815B}.

@@

\subsection{Strengthening the magnetic B-star connection}

>>>>

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018
  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
  of these discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
  class of object known, as well as the most massive
  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
  objects are outliers among outliers; LP 12-502 for instance shows a
  recurring ``dip complex'' with a period and total duration that are
  fixed over more than 1{,}000 cycles, but which in detail showed
  anywhere from four to eight local minima per cycle, and at times
  displayed distinct superposed periods simultaneously.  Broadly
  speaking, we find that none of the CQVs maintain a fixed light curve
  shape over timescales of more than a few hundred cycles, and we
  revisit the arguments for why transient corotating material is the
  most viable explanation.  We expect that our sample will facilitate
  future efforts aimed at connecting these objects to the broader
  contexts of star, disk, and exoplanet evolution. 
  %For instance, if the transiting material is dust, then the rate of
  %dip evolution implies that of order an asteroid belt's worth of mass
  %passes through these structures over their lifetime of
  %$\approx$$10^8$ years.
\end{abstract}

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae \citep{2021isma.book.....B},
occultations by gas-rich circumstellar disks
\citep{2017MNRAS.470..202B}, and, in geometrically favorable
circumstances, eclipses by stars and planets
\citep{2010exop.book...55W}.  More exotic forms of optical variability
relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
both M dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).

Data from K2 and TESS have yielded a new class of variable star whose
root cause is only beginning to become clear: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show nearly periodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z}.
Some CQVs show up to eight local minima (dips) per cycle.  Most are
pre-main-sequence M dwarfs without near-infrared excesses, ages of
$\approx$5-150 million years (Myr), and rotation periods of at most
two days; they are observed to be $\approx$1-3\% of M dwarfs younger
than 100 Myr \citep{2016AJ....152..114R,2022AJ....163..144G}.  The
dips can be chromatic, with a reddening law plausibly consistent with
dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2022ApJ...925...75P,2023ApJ...945..114P}.

A few competing explanations for what causes the complex quasiperiodic
variability are shown in Figure~\ref{fig:f1}.  All young M dwarfs are
spotted, which produces flux variations over characteristic timescales
of the rotation period, $P_{\rm rot}$, and its half-harmonic,
$0.5\,P_{\rm rot}$.  The observed dips occur over durations as short
as $0.05\,P_{\rm rot}$; a ``starspot-only'' scenario can be discarded
for any object with sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The timescales and
amplitudes of the flux variations instead require sharp geometries
with material extrinsic to the stellar surface
\citep[e.g.][]{2017AJ....153..152S,2022AJ....163..144G}.  The
``clump'' scenario invokes opaque dust clumps orbiting near the
Keplerian corotation radius, which periodically eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  The ``prominence''
scenario invokes long-lived condensations of cool and dense
marginally-ionized gas, embedded within the hotter corona, that would
be centrifugally supported near corotation
\citep{1989MNRAS.238..657C,2019MNRAS.482.2853J,2022MNRAS.514.5465W}.
Such structures are analogous to quiescent prominences and filaments
seen in the solar corona \citep[see e.g.][]{2015ASSL..415.....V},
though at much larger relative distances from the stellar surface.  A
final possibility that has been suggested is one of a ``screen'', in
which the inner wall of a quiescent circumstellar disk blocks a
portion of the stellar surface to produce sudden dips whenever spots
come into view \citep{2019ApJ...876..127Z}.

@@

CQVs remain mysterious because they have been both hard to discover
and hard to characterize.   Discoverability is tied to rarity: CQVs
comprise $\approx$1\% of the youngest $\approx$1\% of M dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CQVs have been reported to date
\citep{2016AJ....152..114R,2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2020AJ....160...86B,2022AJ....163..144G,2023ApJ...945..114P}.
The known CQVs are correspondingly faint; the initial K2 discoveries
\citep{2016AJ....152..114R,2017AJ....153..152S} were M2-M6 dwarfs at
distances $\gtrsim$100\,pc, yielding optical brightnesses of
$V$$\approx$15.5 to $V$$>$20.  This renders time-series spectroscopy
at high resolution out of reach for current facilities, despite its
potential utility in ruling between the models.

@@

To assess the completeness of the resulting 120-second cadence data
that is the basis of this study, we cross-matched TIC8
\citep{2018AJ....156..102S} against the Gaia DR2 point-source catalog
\citep{2018A&A...616A...1G}.  We opted for Gaia DR2 rather than DR3
because the base catalog for TIC8 was Gaia DR2, which facilitated a
one-to-one crossmatch using the Gaia source identifiers.  This
exercise showed that for $T$$<$16 M dwarfs, the TESS 2-minute data are
roughly 50\% complete at $\approx$50\,pc.  At $<$20\,pc, $\gtrsim$80\%
of the $T$$<$16 M dwarfs have at least one sector of short-cadence
data; at $>$100\,pc, $\lesssim$10\% of such M dwarfs have at least one
sector of short-cadence data.  Armed with this understanding, we then
used our cross-match between Gaia DR2 and TIC8 to select our stars of
interest, which we defined as stars with 120-second cadence TESS light
curves that satisfied
\begin{align}
  T &< 16 \quad&(\mathrm{Bright\ for\ TESS})\\
  \bprp &> 1.5 \quad&(\mathrm{Red\ stars\ only}) \\
  M_{\rm G} &> 4 \quad&(\mathrm{Dwarf\ stars\ only})  \\
  d &< 150\,{\rm pc} \quad&(\mathrm{Close\ stars\ only}),
\end{align}
for $M_{\rm G} = G + 5\log(\varpi_{\rm as}) + 5$ the Gaia $G$-band
absolute magnitude, $\varpi_{\rm as}$ the parallax in units of
arcseconds, and a geometric distance $d$ defined by inverting the
parallax and ignoring any zero-point correction.  The target sample therefore includes
\nstarssearched\ M dwarfs and late-K dwarfs, down to $T$$<$16 and out
to $d$$<$150\,pc.

@@

With the effective temperatures and stellar radii from the SED fit, we
then estimated the stellar masses by interpolating against the PARSEC
isochrones \citep[v1.2S][]{2014MNRAS.444.2525C}.  The need for models
that incorporate some form of correction for young, active M dwarfs is
well-documented
\citep[e.g.][]{2012ApJ...756...47S,2015ApJ...804..146D,2016A&A...593A..99F,2020ApJ...891...29S}.
Plausible explanations for anomalous M dwarf colors and sizes relative
to model predictions include starspot coverage
\citep[e.g.][]{2017ApJ...836..200G}, and potentially incomplete line
lists \citep[e.g.][]{2013A&A...556A..15R}.  In the PARSEC models,
\citet{2014MNRAS.444.2525C} performed an empirical correction to the
temperature--opacity relation drawn from the BT-Settl model
atmospheres, in order to match observed masses and radii of younq
eclipsing binaries.  This is sufficient for our goal of estimating
stellar masses.  Given our observed $\{ \tilde{T}_{\rm eff},
\tilde{M}_\star, \tilde{t} \}$, and approximating their uncertainties
as Gaussian $\sigma_{\tilde{T}_{\rm eff}}$, $\sigma_{\tilde{M}_\star}$
and $\sigma_{\tilde{t}}$, we evaluate a distance $d$ between our
observations and any model PARSEC grid-point $\{ T_{\rm eff}, M_\star,
t \}$ as
\begin{equation}
  d^2 = 
  \left( \frac{\tilde{T}_{\rm eff} - T_{\rm eff}}{\sigma_{\tilde{T}_{\rm eff}}} \right)^2
  +
  \left( \frac{\tilde{M}_{\star} - M_{\star}}{\sigma_{\tilde{M}_{\star}}} \right)^2
  +
  \left( \frac{\tilde{t} - t}{\sigma_{\tilde{t}}} \right)^2,
\end{equation}
in order to assign equal importance to each dimension.  The preferred
model mass is then one that minimizes this distance, and is quoted in
Table~\ref{tab:thetable}.
{\bf lgb todo: real interpolation, rather than nearest neighbor}

@@

As is typical for CQVs \citep{2017AJ....153..152S}, most CQVs in our
catalog did not show infrared excesses in the WISE1-4 bands.
Visually inspecting the SEDs of our entire \ncpvsfound\ star sample,
we labeled two objects as having ``good'' infrared excesses (both W3
and W4 at $>$3$\sigma$ above the photospheric prediction), and three
as ``possible'' infrared excess (only W3 at $>$3$\sigma$).

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CQVs
for which TESS 120-second cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CQVs in our catalog; for plotting purposes we show
the brightest 27.  We have phased each sector to its own local minimum
because for most of the sources we do not know the period at the
precision necessary to be able to accurately propagate an ephemeris
over two years.
The achievable period precision, $\sigma_P$, can be estimated as
\begin{equation}
  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
  \label{eq:periodprecision}
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline
and $\sigma_{\phi}$ the phase precision with which any one feature
(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day
baseline over a single TESS sector yields $\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the population shown in
Figure~\ref{fig:evoln}; propagated forward 1{,}000 cycles
yields a typical ephemeris uncertainty range of 2-11\,hours.
Measuring the periods for each sector
independently, there did not seem to be any significant ($>$3$\sigma$)
period changes.  This implies an absolute period
stability of $\lesssim$0.1\% over the two-year baseline.

Of the 27 CQVs in Figure~\ref{fig:evoln}, a few show clear signs of
the CQV phenomenon in one sector, and marginal or non-existent signs
in the other.  While there is subjectivity in this assessment, to our
eyes cases for which at least one sector would be flagged as
``ambiguous'' include
TIC~368129164 (Sector 23 might be labeled an EB),
TIC~177309964 (Sector 38 would be simply a rotating star),
TIC~404144841 (Sector 38 looks like a rotating star),
TIC~201898222 (Sector 3 looks like a rotating star),
TIC~144486786 (Sector 32 might be an RS CVn),
and
TIC~38820496 (Sector 28 might be an RS CVn).
TIC~193831684, assessed on a single-sector basis, would probably be
labeled an eclipsing binary---in fact, \citet{2021ApJ...912..123J}
implicitly have already given this source such a label.  However,
based on the the shape evolution between Sectors 13 and 39, it is a
CQV.  
Based on the fraction of sources overall that ``turned off'', the
observed shape evolution implies that CQVs have a duty cycle of
$\approx$75\%.
This type of correction is likely worth including in population-level
estimates of how intrinsically common CQVs are in the low-mass stellar
population \citep[e.g.][]{2022AJ....163..144G}.

@@

The average period, determined by measuring the PDM peak period over
each sector independently, was $\langle P \rangle = 18.5560$\,hr.  The
range between the maximum and minimum sector-specific periods was
measured to be about one minute.   However, in detail, a period shift of
$\pm$1\,minute would yield major phase drifts over the baseline; that
time interval corresponds to roughly 1/1000$^{\rm th}$ of a period,
and we have observed 1500 cycles.  
%Assuming $\sigma_{\phi} \approx
%0.01$ and applying Equation~\ref{eq:periodprecision} yields an
%expected period precision $\sigma_{\rm P} \approx 0.45\,{\rm sec}
%\approx 1.2\times 10^{-4}\,{\rm hr}$. 
 By visually fine-tuning over a
grid in period, we eventually found $P=18.5611 \pm 0.0001$\,hr, which
seems to track certain features in the LP 12-502 light curve well over
the entire dataset.

What exactly is observed?  For the first 64 cycles, the star shows a
pattern reminiscent of an eclipsing binary, with four obvious local
minima.  We dub these dips $\{ 1, 2, 3, 4 \}$ at phases $\{ -0.28,
-0.08, 0, 0.25 \}$, respectively.  Over cycles 0-64, the depth of
dips 1 and 3 remain roughly fixed.  However dip 4 decreases in
depth by about 2\%, while dip 2 increases in depth, by about the
same amount (see Figure~\ref{fig:lp}).  During cycles 48-64, a fifth
dip may also be emerging, in the main ``large'' dip group.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f7.pdf}
		\vspace{-0.1cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are the
      dark blue circles; \nmaybes\ ambiguous CQV candidates are light
      blue circles.  The top panels show the \nstarssearched\ target
      stars with 120-second cadence TESS data as the shaded gray
      background; darker regions correspond to a larger relative
      number of searched stars.  The lower-left panel compares the
      rotation--color distribution of CQVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm cr} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CQV periods, in
      units of hours.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

\subsection{Typical and extreme CQVs}
\label{subsec:extreme}
Figure~\ref{fig:catalogscatter} shows some of the derived properties
for our CQV catalog, and contrasts them against both the target star
sample (top panels), and the population of rotating stars in the Pleiades
from \citet{2016AJ....152..114R}.
Generally, CQVs are much younger than typical field stars. 
In terms of their rotation, relative to the Pleiades,
they are among the more rapidly rotating half of M dwarfs.
The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
to $T$$=$16, is a consequence of the 120-second selection function,
not detection sensitivity.

@@

The most massive CQVs in our sample might represent an interesting new
regime.  To date, the only stars reported to show the CQV phenomenon
are M dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their CAMD
locations, and their membership in LCC.  Based on its light curve
morphology, TIC~405910546 should be studied in greater depth, to
confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
that it has some of the lowest amplitude dips.  While TIC~405754448
might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the depth of
the coherent dips present in the Sector~11 light curve imply that the
CQV signal is indeed from the apparent primary of the system.  Taken
in sum, both of these objects seem to suggest that the CQV phenomenon
extends up in mass to pre-main-sequence K dwarfs.

@@

An instructive point of comparison is the rapidly rotating magnetic
B star, $\sigma$~Ori~E, which shows dips that are deeper in the blue
than in the red \citep{1977ApJ...216L..31H}.  Photometric and
spectroscopic observations of this star have been understood in terms
of a warped torus of circumstellar material, analogous to the
geometries we are discussing for much cooler M dwarfs
\citep{1978ApJ...224L...5L,2005ApJ...630L..81T}.  This material
however is unlikely to be dust, due to the relevant sublimation
timescales.  The opacity is instead thought to be sourced from
bound-free absorption from neutral hydrogen
\citep{2005ApJ...630L..81T}, although to our best knowledge direct
evidence for this conclusion has yet to be acquired.  Separate and
smaller-amplitude emission in $\sigma$~Ori~E may also come from
electrons scattering photospheric light toward the observer when the
clouds are not in transit \citep{2022MNRAS.511.4815B}.

@@

\subsection{Strengthening the magnetic B star connection}

Previous work by \citet{2017AJ....153..152S} noted the possible
connection between the CQVs and rapidly rotating magnetic B stars such
as $\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
distinct from Be-star decretion disks, which do not have any obvious
connection to the stellar magnetic field \citep{2013A&ARv..21...69R}.
